Figure 2 and figure 2 supplementary material

### 2022-03-09 Figures/Figure2.Rmd
add wrapper_corrplots

```{r}
################################################################################
# Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
scatterplot_truevsestimate <- function(merged_data, x, y, title, color, x_lab = "", y_lab = ""){
    merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
    na.omit() -> to_plot

@@

          deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
      }
    }
  }
  }
  results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
}

plot_ridgeplot <- function(data){
 data %>% dplyr::select(-c(ParticipantBarcode, Study)) %>% data.matrix() %>% rcorr() -> cor.table
  final_plot <- list()
  for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
    # select strings to remove from signature names
    substring_remove <- c(paste("_",ct, sep=""),
      "_Tirosh_sigmatrix_SuppFig_3-b",
      "_scRNA-Seq",
      "Fig2ab-",
      "_PBMCs_scRNAseq_sigmatrix",
      "sigmatrix_",
      "_Fig2cd")

@@

  # calculate correlations
 return(plot_ridgeplot(data_toplot))
}
################################################################################
```

@@

>>>>

```{r}
################################################################################
# Customizable corrplot functions (modified from https://www.khstats.com/blog/corr-plots/corr-plots/)
cors <- function(df, cor.stat) {
  M <- Hmisc::rcorr(as.matrix(df), type = cor.stat)
  Mdf <- map(M, ~data.frame(.x))
  return(Mdf)
}

formatted_cors <- function(df, cor.stat){
  cors(df, cor.stat) %>%
    map(~rownames_to_column(.x, var="measure1")) %>%
    map(~pivot_longer(.x, -measure1, "measure2")) %>%
    bind_rows(.id = "id") %>%
    pivot_wider(names_from = id, values_from = value) %>%
    dplyr::rename(p = P) %>%
    mutate(sig_p = ifelse(p < .05, T, F),
           p_if_sig = ifelse(sig_p, p, NA),
           r_if_sig = ifelse(sig_p, r, NA)) 
}
################################################################################

################################################################################
# Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
scatterplot_truevsestimate <- function(merged_data, x, y, title, color, x_lab = "", y_lab = ""){
    merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
    na.omit() -> to_plot

@@

          deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
      }
    }
  }
  }
  results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
}
################################################################################

################################################################################
plot_ridgeplot <- function(data){
 data %>% dplyr::select(-c(ParticipantBarcode, Study)) %>% data.matrix() %>% rcorr() -> cor.table
  final_plot <- list()
  for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
    # select strings to remove from signature names
    substring_remove <- c(paste("_",ct, sep=""),
      "_Tirosh_sigmatrix_SuppFig_3-b",
      "_scRNA-Seq",
      "Fig2ab-",
      "_PBMCs_scRNAseq_sigmatrix",
      "sigmatrix_",
      "_Fig2cd")

@@

  # calculate correlations
 return(plot_ridgeplot(data_toplot))
}
################################################################################

################################################################################
wrapper_corrplots <- function(deconv_data, true_estimates, cancer_abreviation){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))

  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
                                         true_subset_$ParticipantBarcode))

  true_subset <-dplyr::filter(true_subset_, ParticipantBarcode %in% Comm_samples) %>% 
    arrange(factor(ParticipantBarcode, levels = Comm_samples))

  deconv_subset <- dplyr::filter(deconv_data, Samples %in% Comm_samples) %>% 
    arrange(factor(Samples, levels = Comm_samples))

  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
  identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()

  to_corr <- bind_cols(true_subset, deconv_subset_summary) %>% dplyr::select(-c(Samples))
  ct_corrplots <- list()
   for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
    # select strings to remove from signature names
    substring_remove <- c(paste0("_",ct),
      "_Tirosh_sigmatrix_SuppFig_3.b",
      "_scRNA.Seq",
      "Fig2ab.",
      "_PBMCs_scRNAseq_sigmatrix",
      "sigmatrix_",
      "_Fig2cd")

    store_corrs <- tibble(measure1 = character(),
                          measure2 = character(),
                          r = numeric(),
                          n = numeric(),
                          p = numeric(),
                          sig_p = logical(),
                          p_if_sig = numeric(),
                          r_if_sig = numeric())
    # segregate by cancer type
    for (st in unique(to_corr$Study)){
      deconv_ct_names <- dplyr::filter(to_corr, Study == st) %>%
        # segregate by ct
        dplyr::select(matches(ct)) %>%
        formatted_cors(cor.stat = "pearson") %>%
        # reduce to corrs just to ground truth
        dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
        # rename ground truth as cancer type
        dplyr::mutate(measure1 = st)
      #add to the rest of cancer type correlations
      store_corrs <- add_row(store_corrs , deconv_ct_names)
    }

    # Plot
    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|"))) %>% 
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    rotate_x_text(angle = 45)
   }
  return(ct_corrplots)
}

@@

```{r}
wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
```
